---
title: "R Notebook"
output: html_notebook
---



```{r}
library(groundhog)
pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist", "pheatmap", "heatmaply","pheatmap","gplots","RColorBrewer")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analysis/idmPrelimAnal.Rmd")
```

```{r}
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/named.effects.ref.R")
```


```{r}
fullLong <- arrow::read_parquet(here("Data", "longEpMNet.parquet"))
fullShort <- arrow::read_parquet(here("Data","shortEpMNet.parquet"))
fullLong$subID <- as.numeric(fullLong$subID)
fullData <- fullLong %>% full_join(fullShort, by = c("subID"))
```

# Wordcloud

```{r}
#Create a vector containing only the text
text <- as.vector(fullData$memory)
# Create a corpus  
docs <- Corpus(VectorSource(text))
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("the","and"))

dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)

wordcloud(words = df$word, freq = df$freq, min.freq = 1,           max.words=200, random.order=FALSE, rot.per=0.35,            colors=brewer.pal(8, "Dark2"))
```


# H1: People will evaluate more positively, less negatively (i.e., more favorably) on memories with more downstram dependents.

```{r}
m<-glmer(outdegree ~  Val_1 * Val_2 + ( Val_1 + Val_2 | subID), data=fullData,family="poisson")
summary(m)

m<-lmer(Val_1 ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Val_2 ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)
```

# H2: People will be more certain in memories with more downstream dependents.

```{r}
m<-lmer(Cert ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Cert ~  strength + ( strength | subID), data=fullData)
summary(m)
```

# H3: Memories with more dependents will be more clearly defined and accessible.

```{r}
m<-lmer(Clear ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Clear ~  strength + ( strength | subID), data=fullData)
summary(m)
```
# H5: Memories with more dependents will be more fundamental to how people see themselves, and if they were changed, would change the person.

```{r}
m<-lmer(Fund ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Fund ~  strength + ( strength | subID), data=fullData)
summary(m)
```

# H6: Memories with more dependents will be more important to the person.

## To Self

```{r}
m<-lmer(IM ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(IM ~  strength + ( strength | subID), data=fullData)
summary(m)
```

## To Others

```{r}
m<-lmer(IO ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(IO ~  outdegree * indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Val_1","Val_2")) %>% plot()

m<-lmer(IO ~  strength + ( strength | subID), data=fullData)
summary(m)
```

# H9: People’s self-report of retrospected emotions during an experience will be associated with how positively or negatively they perceive the experience.

```{r}
m<-lmer(Often ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)
```

# H11: People think more often about memories with more memories causing them.

# The more memories that depend on a given memory, the more people believe "This memory changed me"

```{r}
m<-lmer(Chan ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  strength + ( strength | subID), data=fullData)
summary(m)
```

# The more memories that depend on a given memory, the more certain that people feel this experience is representative of who they are.

```{r}
m<-lmer(Rep ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Rep ~  strength + ( strength | subID), data=fullData)
summary(m)
```

# Exploratory Analyses

## Sentiment of memory will be associated with dependencies

```{r}
m<-lmer(vad_comp.x ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(vad_comp.x ~  strength + ( strength | subID), data=fullData)
summary(m)

m<-lmer(vad_pos.x ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(vad_pos.x ~  strength + ( strength | subID), data=fullData)
summary(m)

m<-lmer(vad_neg.x ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(vad_neg.x ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer(vad_pos.x ~  indegree*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer(vad_comp.x ~  strength + ( strength | subID), data=fullData)
summary(m)

m<-lmer(vad_pos.x ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(vad_pos.x ~  strength + ( strength | subID), data=fullData)
summary(m)

m<-lmer(vad_neg.x ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(vad_neg.x ~  strength + ( strength | subID), data=fullData)
summary(m)
```




```{r}
m<-lmer(IM ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(IM ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer(IO ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(IO ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-glmer(outdegree ~  Val_1*Val_2 + ( Val_1+Val_2 | subID), data=fullData, family="poisson")
summary(m)
ggpredict(m, terms = c("Val_1","Val_2")) %>% plot()
```


```{r}
m<-lmer(Val_1 ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Val_1 ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer(Val_2 ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Val_2 ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer(Clear ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Clear ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer(Breadth ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Breadth ~  strength + ( strength | subID), data=fullData)
summary(m)
```




```{r}
m<-lmer(Dist ~  outdegree + indegree + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(Dist ~  strength + ( strength | subID), data=fullData)
summary(m)
```

```{r}
m<-glmer(outdegree ~  scale(SO_1) * scale(SO_2) + ( 1 | subID), data=fullData,family="poisson")
summary(m)
ggpredict(m, terms = c("SO_1","SO_2")) %>% plot()
```

```{r}
m<-lmer( Fund ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```


```{r}
fullData$PminN <- (fullData$Val_1-fullData$Val_2)
m<-lmer( PminN ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Fund ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Chan ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Cert ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( IM ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Clear ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Rep ~ SE*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SAM*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ CESD*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SOS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DS*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ MAIA*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DT_P*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DT_M*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ NFC*outdegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SCC*outdegree + ( 1 | subID), data=fullData)
summary(m)
```


## Indegree Cross-Level Interaction

```{r}
fullData$PminN <- (fullData$Val_1-fullData$Val_2)
m<-lmer( PminN ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( PminN ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Fund ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Fund ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Chan ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)
ggpredict(m, terms = c("CESD","indegree")) %>% plot()

m<-lmer( Chan ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)
ggpredict(m, terms = c("SOS","indegree")) %>% plot()

m<-lmer( Chan ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Chan ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
ggpredict(m, terms = c("SCC","indegree")) %>% plot()
```

```{r}
m<-lmer( Cert ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Cert ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( IM ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( IM ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Clear ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Clear ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```

```{r}
m<-lmer( Rep ~ SE*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SAM*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ CESD*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SOS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DS*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ MAIA*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DT_P*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ DT_M*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ NFC*indegree + ( 1 | subID), data=fullData)
summary(m)

m<-lmer( Rep ~ SCC*indegree + ( 1 | subID), data=fullData)
summary(m)
```



# Do people higher in self-esteem have more self than other focused memories?

```{r}
fullData$SminO <- fullData$SO_1 - fullData$SO_2

m<-lmer( SminO ~ SE + ( 1 | subID), data=fullData)
summary(m)
```


```{r}
fullShort <- do.call(data.frame,                      # Replace Inf in data by NA
                   lapply(fullShort,
                          function(x) replace(x, is.infinite(x), NA)))
corMat <- fullShort %>% select(edgeTot:NFC) %>% cor(fullShort,use="pairwise.complete.obs")

outphm <- pheatmap(corMat, fontsize_row = 6, fontsize_col = 6, angle_col = 45, angle_row =45, width=100, height = 200 )

heatmaply_cor(round(corMat,3), Rowv=outphm[[1]], Colv=outphm[[2]], revC=TRUE, fontsize_row = 2.5, fontsize_col = 2.5, angle_col = 45, angle_row =45,  limits = c(-1, 1), colors = colorRampPalette(rev(brewer.pal(n = 7, name =
  "RdYlBu")))(100) )
```

```{r}
fullShort %>% select(vad_comp, MAIA:NFC) %>% corToOne(., "vad_comp")
fullShort %>% select(vad_comp, MAIA:NFC) %>% plotCorToOne(., "vad_comp")
```


```{r}
fullShort %>% select(edgeTot, MAIA:NFC) %>% corToOne(., "edgeTot")
fullShort %>% select(edgeTot, MAIA:NFC) %>% plotCorToOne(., "edgeTot")
```

```{r}
fullShort %>% select(numID, MAIA:NFC) %>% corToOne(., "numID")
fullShort %>% select(numID, MAIA:NFC) %>% plotCorToOne(., "numID")
```

```{r}
fullShort %>% select(dense, MAIA:NFC) %>% corToOne(., "dense")
fullShort %>% select(dense, MAIA:NFC) %>% plotCorToOne(., "dense")
```

```{r}
fullShort %>% select(aveDist, MAIA:NFC) %>% corToOne(., "aveDist")
fullShort %>% select(aveDist, MAIA:NFC) %>% plotCorToOne(., "aveDist")
```

```{r}
fullShort %>% select(Val_1_Homoph, MAIA:NFC) %>% corToOne(., "Val_1_Homoph")
fullShort %>% select(Val_1_Homoph, MAIA:NFC) %>% plotCorToOne(., "Val_1_Homoph")
```

```{r}
fullShort %>% select(Val_2_Homoph, MAIA:NFC) %>% corToOne(., "Val_2_Homoph")
fullShort %>% select(Val_2_Homoph, MAIA:NFC) %>% plotCorToOne(., "Val_2_Homoph")
```

```{r}
fullShort %>% select(Fund_Homoph, MAIA:NFC) %>% corToOne(., "Fund_Homoph")
fullShort %>% select(Fund_Homoph, MAIA:NFC) %>% plotCorToOne(., "Fund_Homoph")
```

```{r}
fullShort %>% select(Rep_Homoph, MAIA:NFC) %>% corToOne(., "Rep_Homoph")
fullShort %>% select(Rep_Homoph, MAIA:NFC) %>% plotCorToOne(., "Rep_Homoph")
```

```{r}
fullShort %>% select(Chan_Homoph, MAIA:NFC) %>% corToOne(., "Chan_Homoph")
fullShort %>% select(Chan_Homoph, MAIA:NFC) %>% plotCorToOne(., "Chan_Homoph")
```










