---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---



```{r}
library(groundhog)
pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist", "pheatmap", "heatmaply","pheatmap","gplots","RColorBrewer", "tm", "wordcloud", "psych")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analysis/idmPrelimAnal.Rmd")
```

```{r}
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/named.effects.ref.R")
```


```{r}
fullLong <- arrow::read_parquet(here("Data", "longEpMNet.parquet"))
fullShort <- arrow::read_parquet(here("Data","shortEpMNet.parquet"))
fullLong$subID <- as.numeric(fullLong$subID)
fullData <- fullLong %>% full_join(fullShort, by = c("subID"))
```

# Descriptives

```{r}
# How many people listed 0 connections?
nrow(fullShort[which(fullShort$edgeTot==0),])

#describe(fullLong$strength)
```

# Wordcloud

```{r}
#Create a vector containing only the text
text <- as.vector(fullData$memory)
# Create a corpus  
docs <- Corpus(VectorSource(text))
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("the","and"))

dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)

set.seed(24)
wordcloud(words = df$word, freq = df$freq, min.freq = 1,           max.words=200, random.order=FALSE, rot.per=0.35,            colors=brewer.pal(8, "Dark2"))
```

# Sanity Checks

## Does time predict number of causes?

Yes, the farther away in time, the more experiences something causes.

```{r}
m<-glmer(outdegree ~  scale(length) + numID + ( scale(length) | subID), data=fullData,family="poisson")
summary(m)
```

## Does time predict causes of experience?

Yes, the farther back in time, the fewer experiences cause something.

```{r}
m<-glmer(indegree ~  scale(length) + numID + ( scale(length) | subID), data=fullData,family="poisson")
summary(m)
```

# H1: People will evaluate more positively, less negatively (i.e., more favorably) on memories with more downstram dependents.

## Valence Self-Report

More positive and negative, experience causes more experience

More positive, experience is caused by more experiences

```{r}
m<-glmer(outdegree ~  scale(positive) + scale(negative) + numID + ( scale(positive) + scale(negative) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(positive) + scale(negative) + numID + ( scale(positive) + scale(negative) | subID), data=fullData,family="poisson")
summary(m)

m<-lmer(positive ~  outdegree + indegree + numID + ( outdegree + indegree | subID), data=fullData)
summary(m)

m<-lmer(negative ~  outdegree + indegree + numID + ( outdegree + indegree | subID), data=fullData)
summary(m)
```

## PANAS

### Outdegree

More positive and more negative, experience causes more experiences

```{r}
m<-glmer(outdegree ~  scale(PANAS_P) + scale(PANAS_N) + numID + ( scale(PANAS_P) + scale(PANAS_N) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_1) + numID + ( scale(PANAS_1) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_2) + numID + ( scale(PANAS_2) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_3) + numID + ( scale(PANAS_3) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_4) + numID + ( scale(PANAS_4) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_5) + numID + ( scale(PANAS_5) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_6) + numID + ( scale(PANAS_6) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_7) + numID + ( scale(PANAS_7) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_8) + numID + ( scale(PANAS_8) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_9) + numID + ( scale(PANAS_9) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(outdegree ~  scale(PANAS_10) + numID + ( scale(PANAS_10) | subID), data=fullData,family="poisson")
summary(m)
```

### Indegree

More positive, more experiences cause an experience

```{r}
m<-glmer(indegree ~  scale(PANAS_P) + scale(PANAS_N) + numID + ( scale(PANAS_P) + scale(PANAS_N) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_1) + numID + ( scale(PANAS_1) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_2) + numID + ( scale(PANAS_2) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_3) + numID + ( scale(PANAS_3) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_4) + numID + ( scale(PANAS_4) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_5) + numID + ( scale(PANAS_5) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_6) + numID + ( scale(PANAS_6) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_7) + numID + ( scale(PANAS_7) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_8) + numID + ( scale(PANAS_8) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_9) + numID + ( scale(PANAS_9) | subID), data=fullData,family="poisson")
summary(m)

m<-glmer(indegree ~  scale(PANAS_10) + numID + ( scale(PANAS_10) | subID), data=fullData,family="poisson")
summary(m)
```

# H2: People will be more certain in memories with more downstream dependents.

Causing more experiences and being caused by more experiences is associated with greater certainty in experience, but causing is a stronger effect.

Using strength/similarity is stronger effect.

```{r}
m<-lmer(scale(Cert) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer(scale(Cert) ~  scale(strengthIn) + scale(strengthOut) + ( scale(strengthIn) + scale(strengthOut) | subID), data=fullData)
summary(m)
```

# H3: Memories with more dependents will be more clearly defined and accessible.

Experiences causing more experiences are more predictive of clarity than experiences caused by more experiences

```{r}
m<-lmer( scale(Clear) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Clear) ~  scale(strengthIn) + scale(strengthOut) + numID + scale(length) + ( scale(strengthIn) + scale(strengthOut) | subID), data=fullData)
summary(m)
```

# H5: Memories with more dependents will be more fundamental to how people see themselves, and if they were changed, would change the person.

The number of an experiences of causes, but not what it is caused by, predict how fundamental an experience is.

```{r}
m<-lmer( scale(Fund) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Fund) ~  scale(strengthIn) + scale(strengthOut) + numID + scale(length) + ( scale(strengthIn) + scale(strengthOut) | subID), data=fullData)
summary(m)
```

## Important principal factor (Changed me, Fundamental, Representative)

```{r}
m<-lmer(scale(PCAimp) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer(scale(PCAimp) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

# H6: Memories with more dependents will be more important to the person.

## To Self

Experiences that cause more experiences are perceived as important to self, but not experiences that are caused by more experiences.

```{r}
m<-lmer( scale(IM) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(IM) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

## To Others

Experiences that cause more experiences are perceived as important to others, but not experiences that are caused by more experiences.

```{r}
m<-lmer( scale(IO) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(IO) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

# More Important to Self than Others

No evidence

```{r}
fullData$ImpDiff <- (fullData$IM-fullData$IO)
m<-lmer( scale(ImpDiff) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)

m<-lmer( scale(ImpDiff) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)
```

# H11: People think more often about memories with more memories causing them.

Experiences with more causes and caused by more are reflected on more frequently. Perhaps some stronger effects for causing more.

```{r}
m<-lmer( scale(Often) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Often) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

# H12: The more memories that depend on a given memory, the more people believe "This memory changed me". Weaker effect for memories with many causes of it.

```{r}
m<-lmer( scale(Chan) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Chan) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

# H13: The more memories that depend on a given memory, the more certain that people feel this experience is representative of who they are.

People feel experiences with more causes are more representative of self. Similar, but weaker, effect for experiences caused by more experiences.

```{r}
m<-lmer( scale(Rep) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Rep) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

# Exploratory Analyses

## Sentiment of memory description will be associated with dependencies

### Combined

Experiences caused by more experiences have more qualitative positive sentiment.

```{r}
m<-lmer( scale(vad_comp) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(vad_comp) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

### Positive

Experiences with more experiences causing them are qualitatively more positive

```{r}
m<-lmer( scale(vad_pos) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(vad_pos) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

### Negative

No negative effects

```{r}
m<-lmer( scale(vad_neg) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(vad_neg) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

## Number of words

No effect of causes or caused by on number of words

```{r}
m<-glmer(nwords ~  outdegree + indegree + numID + scale(length) + ( outdegree + indegree | subID), data=fullData, family="poisson")
summary(m)
```

## Breadth

Experiences with more causes are more broad.

```{r}
m<-lmer( scale(Breadth) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Breadth) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

## Distinctness

Experiences with more causes are perceived as more distinct/different.

```{r}
m<-lmer( scale(Dist) ~  scale(outdegree) + scale(indegree) + numID + scale(length) + ( scale(outdegree) + scale(indegree) | subID), data=fullData)
summary(m)

m<-lmer( scale(Dist) ~  scale(strengthOut) + scale(strengthIn) + numID + scale(length) + ( scale(strengthOut) + scale(strengthIn) | subID), data=fullData)
summary(m)
```

## Do people higher in self-esteem have more self than other focused memories?

```{r}
fullData$SminO <- fullData$SO_1 - fullData$SO_2

m<-lmer( SminO ~ SE + ( 1 | subID), data=fullData)
summary(m)
```

## Page Rank, Hub and Changeability

```{r}
m<-lmer(Chan ~  page + ( page | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  pageW + ( pageW | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  pageOut + ( pageOut | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  pageOutW + ( pageOutW | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  hub + ( hub | subID), data=fullData)
summary(m)

m<-lmer(Chan ~  hubW + ( hubW | subID), data=fullData)
summary(m)
```

```{r}
fullShort <- do.call(data.frame,                      # Replace Inf in data by NA
                   lapply(fullShort,
                          function(x) replace(x, is.infinite(x), NA)))
corMat <- fullShort %>% select(edgeTot:NFC) %>% cor(fullShort,use="pairwise.complete.obs")

outphm <- pheatmap(corMat, fontsize_row = 6, fontsize_col = 6, angle_col = 45, angle_row =45, width=100, height = 200 )

heatmaply_cor(round(corMat,3), Rowv=outphm[[1]], Colv=outphm[[2]], revC=TRUE, fontsize_row = 2.5, fontsize_col = 2.5, angle_col = 45, angle_row =45,  limits = c(-1, 1), colors = colorRampPalette(rev(brewer.pal(n = 7, name =
  "RdYlBu")))(100) )
```

```{r}
fullShort %>% select(vad_compAg, MAIA:NFC) %>% corToOne(., "vad_compAg")
fullShort %>% select(vad_compAg, MAIA:NFC) %>% plotCorToOne(., "vad_compAg")
```


```{r}
fullShort %>% select(edgeTot, MAIA:NFC) %>% corToOne(., "edgeTot")
fullShort %>% select(edgeTot, MAIA:NFC) %>% plotCorToOne(., "edgeTot")
```

```{r}
fullShort %>% select(numID, MAIA:NFC) %>% corToOne(., "numID")
fullShort %>% select(numID, MAIA:NFC) %>% plotCorToOne(., "numID")
```

```{r}
fullShort %>% select(dense, MAIA:NFC) %>% corToOne(., "dense")
fullShort %>% select(dense, MAIA:NFC) %>% plotCorToOne(., "dense")
```

```{r}
fullShort %>% select(aveDist, MAIA:NFC) %>% corToOne(., "aveDist")
fullShort %>% select(aveDist, MAIA:NFC) %>% plotCorToOne(., "aveDist")
```

```{r}
fullShort %>% select(Val_1_Homoph, MAIA:NFC) %>% corToOne(., "Val_1_Homoph")
fullShort %>% select(Val_1_Homoph, MAIA:NFC) %>% plotCorToOne(., "Val_1_Homoph")
```

```{r}
fullShort %>% select(Val_2_Homoph, MAIA:NFC) %>% corToOne(., "Val_2_Homoph")
fullShort %>% select(Val_2_Homoph, MAIA:NFC) %>% plotCorToOne(., "Val_2_Homoph")
```

```{r}
fullShort %>% select(Fund_Homoph, MAIA:NFC) %>% corToOne(., "Fund_Homoph")
fullShort %>% select(Fund_Homoph, MAIA:NFC) %>% plotCorToOne(., "Fund_Homoph")
```

```{r}
fullShort %>% select(Rep_Homoph, MAIA:NFC) %>% corToOne(., "Rep_Homoph")
fullShort %>% select(Rep_Homoph, MAIA:NFC) %>% plotCorToOne(., "Rep_Homoph")
```

```{r}
fullShort %>% select(Chan_Homoph, MAIA:NFC) %>% corToOne(., "Chan_Homoph")
fullShort %>% select(Chan_Homoph, MAIA:NFC) %>% plotCorToOne(., "Chan_Homoph")
```

```{r}
fullShort %>% select(recip, MAIA:NFC) %>% corToOne(., "recip")
fullShort %>% select(recip, MAIA:NFC) %>% plotCorToOne(., "recip")
```

# Cohesive

```{r}
fullShort %>% select(cohes, MAIA:NFC) %>% corToOne(., "cohes")
fullShort %>% select(cohes, MAIA:NFC) %>% plotCorToOne(., "cohes")
```

```{r}
fullShort %>% select(modular, MAIA:NFC) %>% corToOne(., "modular")
fullShort %>% select(modular, MAIA:NFC) %>% plotCorToOne(., "modular")
```


# Reciprocity

```{r}
fullShort %>% select(recip, MAIA:NFC) %>% corToOne(., "recip")
fullShort %>% select(recip, MAIA:NFC) %>% plotCorToOne(., "recip")
```

# Standard Deviation of Degrees

```{r}
fullShort %>% select(sdDeg, MAIA:NFC) %>% corToOne(., "sdDeg")
fullShort %>% select(sdDeg, MAIA:NFC) %>% plotCorToOne(., "sdDeg")
```

```{r}
fullShort %>% select(sdDegW, MAIA:NFC) %>% corToOne(., "sdDegW")
fullShort %>% select(sdDegW, MAIA:NFC) %>% plotCorToOne(., "sdDegW")
```






